Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-17 Manuscript/proof_outline.tex
switch to anonymous, comment out acks

% Anonymous paper:
% \documentclass[sigplan,10pt,anonymous,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

% Paper with authors:
\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

\section*{Acknowledgements}
PP ist partly funded by the Vector foundation, grant
{\em LeanAI (P2022-0241)}.
RD acknowledges the support of the French Ministry of Higher Education and Research and the Hauts-de-France region.

>>>>

% Anonymous paper:
\documentclass[sigplan,10pt,anonymous,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

% Paper with authors:
%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

%\section*{Acknowledgements}
%PP ist partly funded by the Vector foundation, grant
%{\em LeanAI (P2022-0241)}.
%RD acknowledges the support of the French Ministry of Higher Education and Research and the Hauts-de-France region.
